\speculake: Hiding Malware in Speculative Execution

### 2018-12-10 paper/payloads.tex
clear up 'security gained here'

If each jump has the potential to land in up to 1024 possible locations, this
would provide in total $1024^{10} = 2^{100}$ possible keys, or 100~bits of
security. We describe our implementation of nested speculative execution in
Section~\ref{subsec:impl-aes}, where we achieve 128~bits of security.
Figure~\ref{fig:nested-spec} demonstrates this in practice, the trigger program
running a series of training jumps followed by indirect jumps influences the
payload program to follow the same path. Any analyst attempting to follow this
path without the trigger program would need to correctly jump to each of the 10
addresses to load the correct key. The security gained here is not a result of a
single entry point remaining secret but rather multiple independent jumps by the
unknown trigger program providing numerous landing points for each jump.

>>>>

If each jump has the potential to land in up to 1024 possible locations, this
would provide in total $1024^{10} = 2^{100}$ possible keys, or 100~bits of
security. We describe our implementation of nested speculative execution in
Section~\ref{subsec:impl-aes}, where we achieve 128~bits of security.
Figure~\ref{fig:nested-spec} demonstrates this in practice, the trigger program
running a series of training jumps followed by indirect jumps influences the
payload program to follow the same path. Any analyst attempting to follow this
path without the trigger program would need to correctly jump to each of the 10
addresses to load the correct key. The secret key created here is not a result
of a single entry point remaining secret (via the branch predictor) but rather
multiple independent jumps by the unknown trigger program providing numerous
landing points for each jump.
